An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-11 EconGrowth2.Rnw
Now using \twocolumn for the historical data graph.

\usepackage{soul} % Provides strikethrough text
\usepackage{float} % Allows precise positioning of tables and figures within the text
\usepackage{amsmath} % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow} % To create multirow tables
\usepackage{hyperref} % To create hyperlinks in the paper

@@

@@

<<Historical_Lattice_Graph, fig.pos="H", fig.width=3, fig.height=7.0, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot()
@

@@

>>>>

\usepackage{wrapfig}  % Allows wrapping of text around figures
\usepackage{soul}     % Provides strikethrough text
\usepackage{float}    % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}  % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow} % To create multirow tables
\usepackage{hyperref} % To create hyperlinks in the paper

@@

\twocolumn{}
<<Historical_Lattice_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot()
@

@@

@@

\onecolumn{}
